\pkg{Rgbp}: Bayesian Hierarchical Modeling and Frequentist Method Check

### 2013-04-07 jss/article.tex
typo

\subsection{Binomial: 18 Baseball Data}
This dataset contains information about batting averages of 18 major league players through their first 45 official at-bats of the 1970 season (Efron and Morris, 1975). Also, it has one binary covariate indicating whether a player was in the National league (1) or the American league (0). The code below shows a way to make inputs using the first 10 players. One covariate is an indicator variable which is 1 if a player was in the National league and 0 if American league.
\begin{CodeChunk}
\begin{CodeInput}
R> z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11)
R> n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
R> x <- c( 1,  0,  0,  0,  0,  0,  1,  0,  1,  1) 
\end{CodeInput}
\end{CodeChunk}
The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats conditioning on the unknown parameter $p_{j}$: $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$. This dataset is also a part of the package and can be called on \proglang{R} by `\code{R> data(baseball)}'.

\section[Multi-level Structure]{Multi-level Structure}
Hierarchical model is a very powerful tool to (justification of hierarchical model for hierarchical data??)
\\

\code{gbp}, one of functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy is a distribution of observed data and second-level is a conjugate prior distribution on the first-level parameter. Users can determine one of three types of multi-level models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta, based on their datasets. 
\\

@@

where $\mu_{0j} =x_{j}'\beta,~j=1, \ldots, 8$, and $x_{j}$ is $j$-th school's covariate vector ($m\times 1$). Also, $m$ is the number of regression coefficients, which is just 1 for an intercept term if there is no covariate. For reference, a paramter with a zero subscript represents a mean parameter of the prior (second-level) distribution. Also,  Based on this conjugate prior distribution, it is easy to derive corresponding posterior distribution. 
\begin{equation}
\mu_{j}\vert \textbf{y}, \beta, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})\sigma^{2}_{j}),
\end{equation}
where $B_{j}\equiv\frac{\sigma^{2}_{j}}{\sigma^{2}_{j} + A},~j=1, \ldots, 8$ is called a shrinkages and we will explain it in the following section.

@@

\section[Estimation]{Estimation}
\subsection[Shrinkage Estimation]{Shrinkage Estimation}
Estimating shrinkage is a key part of our work because as we can see posterior mean is a linear function of shrinkage and posterior variance is also a linear (Gaussian), quadratic (Poisson), or cubic (Binomial) function of shrinkage. Once we estimate it, we can approximate the posterior moments given only data, for example, $E(\mu_{j}\vert \textbf{y})$ for Gaussian model.
\subsection[ADM]{Adjustment for Density Maximization}
When it comes to estimating a shrinkage, we can notice that it is a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv\frac{\sigma^{2}}{\sigma^{2}+A}=B_{j}(A)$ for Gaussian and $B_{j}\equiv\frac{r}{r+n_{j}}=B_{j}(r)$ for Poisson and Binomial models.
\\

@@

Here Adjustment for Density Maximization (Morris and Tang, 2011), called ADM, comes. It assumes the Beta distribution for shrinkage, which the authors believe is a much better approximation for it, and estimates its posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$.

\subsection[Approximation to Posterior Distribution by Moment Matching]{Approximation to Posterior Distribution via Matching Moments}
After estimating two posterior moments, \code{gbp} reasonably approximates posterior distribution given only data, \emph{i.e.}, ($\mu_{j}\vert \textrm{data}$), ($\lambda_{j}\vert \textrm{data}$), or ($p_{j}\vert \textrm{data}$), by matching two moments with its parameters. The reason we said `reasonablely approximates' is that it is hard to find a closed form of posterior distribution given only data unless it is a Gaussian model. So, we assumed $(p_{j}\vert \textrm{data})$ has also Beta($a_{1}$, $a_{0}$) distribution and matched two estimated moments, $E(p_{j}\vert \textrm{data})$ and $Var(p_{j}\vert \textrm{data})$, with two parameters, $a_{1}$ and $a_{0}$, of this Beta distribution.

@@

\subsection{Unbiased Coverage Probability}
Based on the generated pseudo-datasets, let's define an indicator variable, $I_{ij}$, which is 1 if $j$-th interval estimate from $i$-th pseudo-dataset includes $p_{ij}$ and 0 otherwise. One way to estimate the coverage probability is to take average over those indicator variables. We call it an unbiased coverage probability estimate. For example, $\bar{I}_{1}=\sum_{i=1}^{500}I_{i1}/500$ is the estimated coverage probability for the first player.
\subsection{Rao-Blackwellized Coverage Probability}
Based on the definition of Rao-Blackwellization, we define $E(I_{ij}\vert z_{ij}, r, \beta$) as the Rao-Blackwellized coverage probability, where $r$ and $\beta$ were fixed at first (see 5.1). This expectation is the same as P$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where $\hat{p}_{ij, low}$ and $\hat{p}_{ij, upp}$ are interval estimates (numeric values). We can calculated this probability exactly because we know the distribution of $(p_{ij} \vert z_{ij}, r, \beta)$ is the Beta distribution in (9). For instance, the first player's Rao-Blackwellized coverage probability can be estimated by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$.
\section[Example]{Example}
\subsection[Known Prior Mean]{Known Prior Mean}
Using 10 hospital data with PR
\subsection[Unknown Prior Mean and No Covariate]{Unknown Prior Mean and No Covariate}
Using 8 school data with GR
\subsection[Unknown Prior Mean and One Covariate]{Unknown Prior Mean and One Covariate}
Using 18 baseball data with BR

>>>>

\subsection{Binomial: 18 Baseball Data}
This dataset contains information about batting averages of 18 major league players through their first 45 official at-bats of the 1970 season (Efron and Morris, 1975). Also, it has one binary covariate indicating whether a player was in the National league (1) or in the American league (0). The code below shows a way to make inputs using the first 10 players. \begin{CodeChunk}
\begin{CodeInput}
R> z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11)
R> n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
R> x <- c( 1,  0,  0,  0,  0,  0,  1,  0,  1,  1) 
\end{CodeInput}
\end{CodeChunk}
The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats conditioning on the unknown parameter $p_{j}$: $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$. This dataset is also a part of the package and can be called on \proglang{R} by `\code{R> data(baseball)}'.

\section[Multi-level Structure]{Multi-level Structure}
Multi-level model is a very powerful tool for explaining the hierarchical sturucture in data, for example, with student-level, school-level, and district-level information. \code{gbp}, one of functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy is a distribution of observed data and second-level is a conjugate prior distribution on the first-level parameter. Users can determine one of three types of multi-level models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta, based on their datasets. 
\\

@@

where $\mu_{0j} =x^{T}_{j}\beta,~j=1, \ldots, 8$, $x_{j}$ is $j$-th school's covariate vector ($1\times m$), and $m$ is the number of regression coefficients which is just 1 for an intercept term if there is no covariate. For reference, a paramter with a zero subscript, $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution. Also,  Based on this conjugate prior distribution, it is easy to derive corresponding posterior distribution. 
\begin{equation}
\mu_{j}\vert \textbf{y}, \beta, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})\sigma^{2}_{j}),
\end{equation}
where $B_{j}\equiv\frac{\sigma^{2}_{j}}{\sigma^{2}_{j} + A},~j=1, \ldots, 8$, is called a shrinkages.

@@

\section[Estimation]{Estimation}
\subsection[Shrinkage Estimation]{Shrinkage Estimation}
Estimating shrinkage is a key part of our work because as we can see the posterior means in (3), (6), and (9) are a linear function of shrinkage and the posterior variances are also a linear (Gaussian), quadratic (Poisson), or cubic (Binomial) function of shrinkage. Once we estimate it, we can approximate the posterior moments given only data by Adam's law, for example, $E(\mu_{j}\vert \textbf{y})=E(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ for Gaussian model and by Eve's law, for instance, $Var(\mu_{j}\vert \textbf{y})=E(Var(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$
\subsection[ADM]{Adjustment for Density Maximization}
When it comes to estimating a shrinkage, we can notice that it is a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv\frac{\sigma^{2}}{\sigma^{2}+A}=B_{j}(A)$ for Gaussian and $B_{j}\equiv\frac{r}{r+n_{j}}=B_{j}(r)$ for Poisson and Binomial models.
\\

@@

Here the adjustment for density maximization (Morris and Tang, 2011), called ADM, comes. It assumes the Beta distribution for shrinkage, which the authors believe is a much better approximation for it, and estimates its posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$.

\subsection[Approximation to Posterior Distribution by Moment Matching]{Approximation to Posterior Distribution via Matching Moments}
After estimating two posterior moments, \code{gbp} reasonably approximates posterior distribution given only data, \emph{i.e.}, ($\mu_{j}\vert \textrm{data}$), ($\lambda_{j}\vert \textrm{data}$), or ($p_{j}\vert \textrm{data}$), by matching two moments with its parameters. The reason we said `reasonablely approximates' is that it is hard to find a closed form of posterior distribution given only data unless it is a Gaussian model. So, we assumed $(p_{j}\vert \textrm{data})$ had also Beta($a_{1}$, $a_{0}$) distribution and matched two estimated moments, $E(p_{j}\vert \textrm{data})$ and $Var(p_{j}\vert \textrm{data})$, with two parameters, $a_{1}$ and $a_{0}$, of this Beta distribution.

@@

\subsection{Unbiased Coverage Probability}
Based on the generated pseudo-datasets, let's define an indicator variable, $I_{ij}$, which is 1 if $j$-th interval estimate from $i$-th pseudo-dataset includes $p_{ij}$ and 0 otherwise. One way to estimate the coverage probability is taking average over these indicator variables. We call it an unbiased coverage probability estimate. For example, $\bar{I}_{1}=\sum_{i=1}^{500}I_{i1}/500$ is the estimated coverage probability for the first player.
\subsection{Rao-Blackwellized Coverage Probability}
Based on the definition of Rao-Blackwellization, we define $E(I_{ij}\vert z_{ij}, r, \beta$) as the Rao-Blackwellized coverage probability, where $r$ and $\beta$ were fixed at first (see 5.1). This expectation is the same as P$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where $\hat{p}_{ij, low}$ and $\hat{p}_{ij, upp}$ are interval estimates (numeric values). We can calculated this probability exactly because we know the distribution of $(p_{ij} \vert z_{ij}, r, \beta)$ is the Beta distribution in (9). For instance, the first player's Rao-Blackwellized coverage probability can be estimated by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$.
\section[Example]{Example}
\subsection[Known Prior Mean]{Known Prior Mean}
Using 10 hospital data with PR
\subsection[Unknown Prior Mean and No Covariate]{Unknown Prior Mean and No Covariate}
Using 8 school data with GR
\subsection[Unknown Prior Mean and One Covariate]{Unknown Prior Mean and One Covariate}
Using 18 baseball data with BR
